Postural developments mediate children's visual access to social information

### 2018-01-27 writeup-cogsci/cogsci2018_faceOnly.Rmd

To formalize these observations, we fit a generalized linear model to the proportion faces seen each infant in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) model can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p =`r round(faceGLMOut$coef[2,4],2)`).  We found the same pattern of results for the OpenPose detections, omitted here for brevity. With respect to wrist/hand detections,  we also found the same pattern with respect to infant's visual access to hands (see Table 4); including interaction terms also reduced any main effect of age on the proportion of hands detected ((b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)` , p =`r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants' access to faces is heavily infleunced by their postural and locomotive developments.

@@

# General Discussion
We use a head-mounted camera to explore how children's postural and locomotive development directly impacts their access to social information, here operationalized as the presence of the faces and wrists of their caregiver. We found that children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically impacted the proportion of faces and wrists that were avaliable in the child's visual field. Thus, infants' postural and locomotive developments are mediating factors that explain some of the age-related changes in the proportion of faces and hands avaliable in infants' visual field.

Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.
This work also deploys novel advancements in computer vision to the study of developmental psychology. The field of object detection and recognition has advanced dramatically in the past five years since the re-birth of deep learning algorithms [@krizhevsky2012imagenet], creating a new generation of algorithmic tools. These tools are substantially better equipped to deal with noisier, more complicated datasets and can extract richer and more detailed information. Videos from the infant perspective provided substantial challenges (e.g., partially occluded faces) for the classic models of face detection (e.g., ViolaJones) [@viola2004robust].  Further, as the headcam technologies employed here were inexpensive (~$60 a camera) and the computer vision algorithms freely avaliable, this method is a promising avenue for quanitfying the visual and social information avaliable to infant learners.

>>>>

To formalize these observations, we fit a generalized linear model to the proportion faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) model can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p =`r round(faceGLMOut$coef[2,4],2)`).  We found the same pattern of results for the OpenPose face detections, omitted here for brevity. We also found the same pattern with respect to infant's visual access to hands (see Table 4); including interaction terms also reduced any main effect of age on the proportion of hands detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)` , p =`r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants access to social information is heavily infleunced by their postural and locomotive development.

@@

# General Discussion
We use a head-mounted camera to explore how children's postural and locomotive development directly impacts their access to social information, here operationalized as the presence of the faces and wrists of their caregiver. We found that children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically impacted the proportion of faces and wrists that were avaliable in the child's visual field. Thus, infants' postural and locomotive developments are mediating factors that explain some of the age-related changes in the proportion of faces and hands avaliable in infants' visual field. Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

This work also deploys novel advancements in computer vision to the study of developmental psychology. The field of object detection and recognition has advanced dramatically in the past five years since the re-birth of deep learning algorithms [@krizhevsky2012imagenet], creating a new generation of algorithmic tools. These tools are substantially better equipped to deal with noisier, more complicated datasets and can extract richer and more detailed information. Videos from the infant perspective provided substantial challenges (e.g., partially occluded faces) for the classic models of face detection (e.g., ViolaJones) [@viola2004robust].  Further, as the headcam technologies employed here were inexpensive (~$60 a camera) and the computer vision algorithms freely avaliable, this method is a promising avenue for quanitfying the visual and social information avaliable to infant learners.
